Spin canonical divisors of log stacky curves

### 2015-06-24 stacky_write_up/spin_cring.tex
sat-three-induction fix

\begin{lem}
\label{lem:sat-two-induction-genus-0}
\todo{Make explicit assumptions on genus.}
Suppose $L'$ is a log half-canonical divisor of $\sx$ with course space $X$ of genus 0 such that $sat(Eff(\halfcan')) = 3$ with $R_{\halfcan'} = k[x_3, x_4
, x_5,\ldots, x_m]/I'$.  Let $L = L' + \frac{1}{
3}P$.  Suppose $\deg x_i = i$ for $i \in \{3, 4, 5\}$ and that the ordering on $k[x]$ satisfies
\begin{align*}
	\ord_{x_3}(f) < \ord_{x_3}(h) \implies f \prec h.
\end{align*}
Then, the following statements hold.

@@

\ssec{Base Cases}
\label{ssec:g_0_base}
Now we have an inductive statement on the number of ramified
points in Lemma ~\ref{lem:sat_three_induction} and
an inductive statement on stabilizer orders in Theorem
~\ref{thm:ram_order_ind}. After verifying that explicit pairs
$(\sx, J)$ of stacky curves $\sx$ with particular signatures and
particular choices of $J$ are admissible, the application of the
two inductive statements demonstrate that the spin canonical ring
$R(\sx , 0, L)$ is generated in degree at most $e := \max(5, e_1,
\ldots, e_r)$ with relations generated in degree at most $2e$ for
$\sx$ with any signature $\sigma = (0; e_1, \ldots , e_r; 0)$ outside
of a finite set of exceptional cases.

@@

Through the application of two processes of induction, by adding 
points via Lemma ~\ref{lem:sat_three_induction} and by raising
stabilizer orders via Theorem ~\ref{thm:ram_order_ind},
we obtain Theorem ~\ref{thm:g_0_generators_relations} for any tame
log spin curve $(\sx, \Delta, L)$ over a perfect field $k$ with
signature $\sigma$ covered by this induction process.
In particular, this induction process covers all signatures $\sigma
= (0; e_1, \ldots, e_r; 0)$ such that either $r \geq 5$ or
for some listed base case $(\sigma', J)$ with $\sigma' = (0; e_1',
\ldots, e_r'; 0)$, $e_i \geq e_i'$ for all $i$.
Before we prove the main theorem, we describe the cases not be
covered by induction.

@@

If $r > 5$, then we can use Lemma
~\ref{lem:sat_three_induction} to add ramified points with
stabilizer order $3$ to case (k) of Lemma
~\ref{lem:g_0_admissible_cases}, which corresponds to $\sigma_{11}
= (0; 3, 3, 3, 3, 3; 0), J_{11} = \{1, 2, 3, 4, 5\}$. This case
clearly satisfies the conditions of Lemma
~\ref{lem:sat_three_induction} (recall from Subsection ~\ref
{ssec:g_0_saturation} that saturation is 3 here), and the
immediate consequence of parts (a) and (c) of Lemma
~\ref{lem:sat_three_induction} is that any $R(\sx', \Delta,
\halfcan')$ corresponding to signatures $\sigma'$ with ramification
orders all equal to $3$ for any $r > 5$ is generated up to
degree $e := \max(5, e_1', \ldots, e_r')$ with relations generated
up to degree $2e$. Furthermore, Lemma ~\ref{lem:n-3s-admissible}
implies that these cases satisfy all of the conditions of Theorem
~\ref{thm:ram_order_ind}.

>>>>

\begin{lem}
\label{lem:sat-three-induction-g-0}
\todo{Make explicit assumptions on genus.}
Suppose $L'$ is a log half-canonical divisor of $\sx$ with course space $X$ of genus 0 such that $sat(Eff(\halfcan')) = 3$ with $R_{\halfcan'} = k[x_3, x_4
, x_5,\ldots, x_m]/I'$.  Let $L = L' + \frac{1}{
3}P$.  Suppose $\deg x_i = i$ for $i \in \{3, 4, 5\}$ and that the ordering on $k[x]$ satisfies
\begin{align*}
	\ord_{x_3}(f) < \ord_{x_3}(h) \implies f \prec h.
\end{align*}
Then, the following statements hold.

@@

\ssec{Base Cases}
\label{ssec:g_0_base}
Now we have an inductive statement on the number of ramified
points in Lemma ~\ref{lem:sat-three-induction-g-0} and
an inductive statement on stabilizer orders in Theorem
~\ref{thm:ram_order_ind}. After verifying that explicit pairs
$(\sx, J)$ of stacky curves $\sx$ with particular signatures and
particular choices of $J$ are admissible, the application of the
two inductive statements demonstrate that the spin canonical ring
$R(\sx , 0, L)$ is generated in degree at most $e := \max(5, e_1,
\ldots, e_r)$ with relations generated in degree at most $2e$ for
$\sx$ with any signature $\sigma = (0; e_1, \ldots , e_r; 0)$ outside
of a finite set of exceptional cases.

@@

Through the application of two processes of induction, by adding 
points via Lemma ~\ref{sat-three-induction-g-0} and by raising
stabilizer orders via Theorem ~\ref{thm:ram_order_ind},
we obtain Theorem ~\ref{thm:g_0_generators_relations} for any tame
log spin curve $(\sx, \Delta, L)$ over a perfect field $k$ with
signature $\sigma$ covered by this induction process.
In particular, this induction process covers all signatures $\sigma
= (0; e_1, \ldots, e_r; 0)$ such that either $r \geq 5$ or
for some listed base case $(\sigma', J)$ with $\sigma' = (0; e_1',
\ldots, e_r'; 0)$, $e_i \geq e_i'$ for all $i$.
Before we prove the main theorem, we describe the cases not be
covered by induction.

@@

If $r > 5$, then we can use Lemma
~\ref{sat-three-induction-g-0} to add ramified points with
stabilizer order $3$ to case (k) of Lemma
~\ref{lem:g_0_admissible_cases}, which corresponds to $\sigma_{11}
= (0; 3, 3, 3, 3, 3; 0), J_{11} = \{1, 2, 3, 4, 5\}$. This case
clearly satisfies the conditions of Lemma
~\ref{sat-three-induction-g-0} (recall from Subsection ~\ref
{ssec:g_0_saturation} that saturation is 3 here), and the
immediate consequence of parts (a) and (c) of Lemma
~\ref{sat-three-induction-g-0} is that any $R(\sx', \Delta,
\halfcan')$ corresponding to signatures $\sigma'$ with ramification
orders all equal to $3$ for any $r > 5$ is generated up to
degree $e := \max(5, e_1', \ldots, e_r')$ with relations generated
up to degree $2e$. Furthermore, Lemma ~\ref{lem:n-3s-admissible}
implies that these cases satisfy all of the conditions of Theorem
~\ref{thm:ram_order_ind}.
